---
title: "BiocPkgStatus: longitudinal database of package check outcomes"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{BiocPkgStatus: longitudinal database of package check outcomes}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup,message=FALSE,results="hide",echo=FALSE}
library(BiocPkgStatus)
```

# Introduction

The BiocBuildTools package (github: vjcitn/BiocBuildTools) has prototypical
code for checking all packages and storing results in SQLite.

To get a version of the database,
point a  browser to [https://tinyurl.com/3hbvaejj](https://tinyurl.com/3hbvaejj) and download the SQLite
file found there.

Set environment variable BIOC_PKG_STATUS_SQLITE to the path where the SQLite file was stored.

# Basic queries

We work with the database as follows:

```{r do1}
library(BiocPkgStatus)
con = status_db()
con |> dbListTables()
```

The `basic` table has a listing of package commit and check times.
```{r lkbasic}
con |> tbl("basic") |> head(10)
con |> tbl("basic") |> filter(package=="parody")
```

Tables `error`, `warnings` and `notes` are from `rcmdcheck::rcmdcheck` applied
with no additional parameters.  `desc` contains data from DESCRIPTION for
each package at time of check.  `BcChkERR` and `BcChkWARN` are from
BiocCheck::BiocCheck.

```{r lkbc}
con |> tbl("BcChkERR") |> filter(type=="checkVigInstalls")
RSQLite::dbDisconnect(con)
```
